\documentclass[line,margin]{res}

\begin{document}

\name{Milo Quinn Swanson Gertjejansen}

\address{17460 Barrington Court, Minnetonka, MN 55345}
\address{(952) 412-5004, milo@milogert.com}


\begin{resume}

\section{OBJECTIVE}

To obtain an entry level programming position in a Computer Science-related position that will allow me to make meaningful contributions to the field.


\section{EDUCATION}

{\bf Michigan Technological University,} Houghton, MI \hfill Fall 2012 - present \\
{\sl B. S. in Computer Science,} Major GPA: 3.5, Overall GPA: 3.6 \\
Expected graduation May 2015

{\bf Normandale Community College,} Bloomington, MN \hfill Fall 2011 - Spring 2012 \\
Transferred to Normandale Fall 2011 for generals \\
{\sl Generals:} Transferred to Michigan Technological University for Computer Science

{\bf Hennepin Technical College,} Eden Prairie, MN \hfill Fall 2009 - Spring 2011 \\
{\sl Programming:} Transferred to Normandale Community College for generals\\
{\sl Audio Recording Production Specialist:} Switched majors to programming


\section{WORK EXPERIENCE}

{\bf Enterprise License Key Management Intern} \hfill Summer 2014 \\
{\sl Ford Motor Company}, Dearborn, MI
\begin{itemize}

  \itemsep -2pt % reduce space between items

  \item Worked with license keys for Ford on a global scale as well as analyzing usage metrics.
  \item Redesigned my team's SharePoint site to better allow buisness IT to collaborate with the team.

\end{itemize}

{\bf Student Web Content Specialist} \hfill September 2013 - Present \\
{\sl UMC, Michigan Technological University}, Houghton, MI
\begin{itemize}

  \itemsep -2pt %reduce space between items

  \item Worked as a web editor for University Marketing and Communications at MTU.
  \item Worked primarily within the Rhythmix CMS to keep the MTU webpage up to date.

\end{itemize}

{\bf Software Development Intern} \hfill November 2011 - August 2013 \\
{\sl MediaBeacon LLC}, Minneapolis, MN
\begin{itemize}

  \itemsep -2pt % reduce space between items

  \item Found and fixed bugs in digital asset management software.
  \item Recieved statements of work and developed code for parts of them.

\end{itemize}


\section{COMPUTER SKILLS}

{\bf Languages:} C, C++, Java, Python, zsh (bash), HTML, CSS, JavaScript, LaTeX \\
{\bf Libraries:} MongoDB, Flask, jdbc, MySQLdb (Python), sqlite (Python), jinja2 (and similar) templates \\
{\bf Applications:} Cygwin, gcc, g++, Eclicpse, JetBrains suite, Sublime Text \\
{\bf Operating Systems:} Microsoft Windows, Linux (command line and GUI), and Mac OS X (command line a GUI) \\
{\bf Website:} Host a website (http://milogert.com) for projects of my own.


\section{AWARDS AND ACHIEVEMENTS}

Received the honor of earning Eagle Scout in the Boy Scouts of America \\
Have a consecutive 3.5+ GPA through all years of college \\
Secretary on Michigan Technological University’s McNair Hall Association \\
Web Developer on Michigan Technological University’s Broomball Committee

\end{resume}

\end{document}
